A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-05-03 report_clean/intro.tex
fixed extra stupid bugs

Before proceeding, let us define the geometrical setting of the problem. We consider the frequency domain problem (\ref{eq:model_freq_domain}) posed in the domain $(-L,\;\infty)\times\mathbb{R},\; L>0$, with the 
 boundary conditions chosen as follows. At the left boundary of the domain, which represents the wall of the Tokamak, we pose Robin boundary conditions 
\be
\label{eq:boundary_conditions_intro}
curl \hat{\mathbf{E}} -i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} -\imath\lambda\E_{inc}\wedge \n,
\ee
where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and $\lambda$ is 
the frequency of the antenna. We truncate the domain 
$(-L,\; \infty)\times\mathbb{R}$ to $(-L,\; H)\times\mathbb{R},\; H>0,$ and set on the right boundary $\operatorname{curl} \hat{\E} = 0$.

@@

Second, we briefly develop an original scheme based on widely appreciated semi-lagrangian schemes
for the discretization of time domain Maxwell's equations with a linear current.
Thirdly, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization of \eqref{eq:main_model}, suggested in \cite{stable_yee_plasma_current}. 
We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{\mrev{-i\omega} t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
\urev{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
In application to a non-resonant case of (\ref{eq:main_frequency_domain_intro}), equipped with boundary conditions, the limited absorption principle states that the solution of (\ref{eq:seq_regularized}) would coincide with the solution of (\ref{eq:main_frequency_domain_intro})
as $\nu\rightarrow 0\pm$. Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_model}) 
states that if the boundary conditions are chosen harmonic in time, e.g. $\left.\partial_x E_y\right|_{x=-L}=\mathrm{e}^{-i\omega_{*} t}$, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
tends to a steady state of the form $ \left(\mathbf{E}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
$\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
in the frequency domain, with $\omega=\omega_{*}$ and the boundary condition $\left.\partial_x \hat{E}_y\right|_{x=-L}=1$. For more details see e.g. \cite{Morawetz, Eidus}. The commutation between the two principles then write as}
$$
\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0},
$$
see Figure \ref{fig:limits}. 
Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in our case due to the singularity
of the hybrid resonance.
\begin{figure}
\begin{tikzpicture}
   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
    \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
     };
 \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow+\infty$} (m-2-1);
  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
 \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow +\infty$} (m-2-2);

>>>>

Before proceeding, let us define the geometrical setting of the problem. We consider the frequency domain problem (\ref{eq:model_freq_domain}) posed in the domain $(-L,\;\infty)\times\mathbb{R},\; L>0$, with the 
 boundary conditions chosen as follows. At the left boundary of the domain, which represents the wall of the Tokamak, we pose Robin boundary conditions 
\be
\label{eq:boundary_conditions_intro}
curl \hat{\mathbf{E}} -i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} -\imath\lambda\E_{inc}\wedge \n,
\ee
where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and \mrev{$\lambda\geq 0$} is 
the frequency of the antenna. We truncate the domain 
$(-L,\; \infty)\times\mathbb{R}$ to $(-L,\; H)\times\mathbb{R},\; H>0,$ and set on the right boundary $\operatorname{curl} \hat{\E} = 0$.

@@

Second, we briefly develop an original scheme based on widely appreciated semi-lagrangian schemes
for the discretization of time domain Maxwell's equations with a linear current.
Thirdly, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization of \eqref{eq:main_model}, suggested in \cite{stable_yee_plasma_current}. 
We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{\mrev{-i\omega} t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
\urev{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
In application to a non-resonant case of (\ref{eq:main_frequency_domain_intro}), equipped with boundary conditions, the limited absorption principle states that the solution of (\ref{eq:seq_regularized}) would coincide with the solution of (\ref{eq:main_frequency_domain_intro})
as $\nu\rightarrow 0$. Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_model}) 
states that if the boundary conditions are chosen harmonic in time, e.g. $\left.\partial_x E_y\right|_{x=-L}=\mathrm{e}^{-i\omega_{*} t}$, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
tends to a steady state of the form $ \left(\mathbf{E}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
$\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
in the frequency domain, with $\omega=\omega_{*}$ and the boundary condition $\left.\partial_x \hat{E}_y\right|_{x=-L}=1$. For more details see e.g. \cite{Morawetz, Eidus}. The commutation between the two principles then write as}
$$
\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0},
$$
see Figure \ref{fig:limits}. 
Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in our case due to the singularity
of the hybrid resonance.
\begin{figure}
\begin{tikzpicture}
   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
    \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
     };
 \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow+\infty$} (m-2-1);
  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
 \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow +\infty$} (m-2-2);
